%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\chapter {\Large{About Siminov}}

Siminov is a open source framework build and managed by Siminov Software Solution LLP and its community. It is a free software that is distributed under the Apache License, Version 2.0 (the "License"). Aim of this framework is to reduce time and effort spend in building mobile application on various platforms like (Android, iOS, Blackberry, Windows).

Siminov Framework is build by combining various Siminov products like (Siminov ORM , Siminov Hybrid, Siminov Konnect). These components are available or in development stage on all platforms.

\section{Siminov Android ORM}
Siminov Android ORM is an object-relational mapping (ORM) library for the Native Android Java language, providing a framework for mapping an object-oriented domain model to a traditional relational database. It primary maps Android Java classes to database tables (and from Java data types to SQLite data types.). It also provides data query and retrieval facilities. It also generates the SQLite calls and attempts to relieve the developer from manual result set handling and object conversion and keep the application protable to all supported SQLite databases with little performance overhead.


\section{Siminvo Hybrid}
Siminov Hybrid is build using Siminov Android ORM Framework and Siminov JavaScript Framework, together it enables application to map JavaScript/Java object to relational database. Using this application developer can build application which uses the best of both Native and Web technology.

Siminov Hybrid not only take care of mapping from JavaScript/Java  classes to database tables (and from JavaScript/Java data types to SQL data types), but also provides data query and retrieval facilities.

