%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\chapter {\Large{Building Application}}
Building application based on Siminov Android ORM/Siminov Hybrid Framework is easy and simple. By the help of \textbf{Siminov Hybrid Template Application} we will explain how we can build application.


\section{Configure ApplicationDescriptor.si.xml}
Application Descriptor is the one who connects application to Siminov Framework. It provide basic information about application, which defines the behaviour of application.

	\lstinputlisting[language=xml]{Resources/siminov_hybrid_template_application_application_descriptor.txt}



\section{Configure DatabaseDescriptor.si.xml}
Database Descriptor is the one who defines the schema of database.

	\lstinputlisting[language=xml]{Resources/siminov_hybrid_template_application_database_descriptor.txt}


\section{Configure LibraryDescriptor.si.xml}
Library Descriptor is the one who denes the properties of library.


	\lstinputlisting[language=xml]{Resources/siminov_library_template_library_descriptor.txt}


\section{Configure DatabaseMappingDescriptor.si.xml}
Database Mapping Descriptor is one which does ORM, it maps POJO class to database table.

	\lstinputlisting[language=xml]{Resources/siminov_hybrid_template_application_database_mapping_descriptor.txt}



\section{Using Annotation}
Liquor pojo class of Siminov template application.

	\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_liquor_pojo_class.txt}


\section{Saving Entity Object}
Saving liquor entity object.

	\begin{enumerate}

		\item \small \textbf{Java}
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_saving_java_liquor_object.txt}

	
		\item \small \textbf{JavaScript}
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_saving_javascript_liquor_object.txt}


	\end{enumerate}



\section{Updaing Entity Object}
Updating liquor object.

	\begin{enumerate}

		\item \small \textbf{Java}
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_updating_java_liquor_object.txt}

	
		\item \small \textbf{JavaScript}
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_updating_javascript_liquor_object.txt}

	\end{enumerate}



\section{Save Or Update Entity Object}
Save or update liquor object.

	\begin{enumerate}

		\item \small \textbf{Java} 
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_save_or_update_java_liquor_object.txt}

	
		\item \small \textbf{JavaScript}
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_save_or_update_javascript_liquor_object.txt}


	\end{enumerate}




\section{Deleting Entity Object}
Deleting liquor object.

	\begin{enumerate}

		\item \small \textbf{Java}
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_deleting_java_liquor_object.txt}


		\item \small \textbf{JavaScript}
			\lstinputlisting[language=Java]{Resources/siminov_hybrid_template_application_deleting_javascript_liquor_object.txt}

	\end{enumerate}




