%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\addcontentsline{toc}{chapter}{Preface}
\begin{flushleft}
	\textbf{\emph{\Large{Preface}}}
\end{flushleft}


\small
A hybrid application, by definition is derived from a combination of technologies, approaches or elements of different kinds. With respect to mobile applications, a hybrid application leverages best of both native and mobile web technologies. 

In hybrid environment, it is very difficult to  map JavaScript/Java objects to relational database, but Siminov makes application developer life easy and simiple by mapping JavaScript/Java objects to relational database.



\begin{center}
	\colorbox{grey}{
		\parbox[t]{.8\linewidth}{
			\fontsize{11pt}{11pt}\selectfont % The first argument for fontsize is the font size of the text and the second is the line spacing - you may need to play with these for your particular title
			\vspace*{0.7cm} % Space between the start of the title and the top of the grey box
		
			\hfill \textbf{Note} \\
			\hfill While having a strong background in SQL is not required to use Android-Siminov Framework, having a basic understanding of the concepts can greatly help you understand Siminov more fully and quickly. Probably the single best background is an understanding of data modeling principles. You might want to consider these resources as a good starting point: \url{http://en.wikipedia.org/wiki/Data_modeling}\\
		
			\vspace*{0.7cm} % Space between the end of the title and the bottom of the grey box
		}
}

\end{center}


Siminov not only takes care of the mapping from JavsScript/Java classes to database tables (and from JavaScript/Java data types to SQL data types), but also provides data query and retrieval facilities. It can significantly reduce development time otherwise spent with manual data handling in SQLite. Siminov design goal is to relieve the developer from 99\% of common data persistence-related programming tasks by eliminating the need for manual, hand-crafted data processing using SQLite. However, unlike many other persistence solutions, Siminov does not hide the power of SQLite from you and guarantees that your investment in relational technology and knowledge is as valid as always.

Siminov may not be the best solution for data-centric applications that only use stored-procedures to implement the business logic in the database, it is most useful with Hybrid object-oriented domain models and business logic in the JavaScript/Java based. However, Siminov can certainly help you to remove or encapsulate vendor-specific SQLite code and will help with the common task of result set translation from a tabular representation to a graph of objects.



\section{Get Involved}

Use Siminov and report any bugs or issues you find. Try your hand at fixing some bugs or implementing enhancements. Engage with the community using mailing lists, forums, IRC, or other ways listed at \url{https://github.com/Siminov}. Help improve or translate this documentation. Contact us on the developer mailing list if you have interest. Spread the word. Let the rest of your organization know about the benefits of Siminov Framework.

\textbf{\large{Siminov Native ORM}}

\begin{enumerate} 

	\item \textbf{Web Site}: \url{https://siminov.github.io.com/android-orm} 
	
	\item \textbf{Github Website}: \url{https://github.com/Siminov/android-orm} 

	\item \textbf{Wiki}: \url{https://github.com/Siminov/android-orm/wiki}

	\item \textbf{Issue Tracker}: \url{https://github.com/Siminov/android-orm/issues} 

\end{enumerate}



\textbf{\large{Siminov Hybrid ORM Framework}} 

\begin{enumerate} 
	
	\item \textbf{Web Site}: \url{https://siminov.github.io.com/android-hybrid} 

	\item \textbf{Github Website}: \url{https://github.com/Siminov/android-hybrid} 

	\item \textbf{Wiki}: \url{https://github.com/Siminov/android-hybrid/wiki}

	\item \textbf{Issue Tracker}: \url{https://github.com/Siminov/android-hybrid/issues} 

\end{enumerate}




\section{Getting Started Guide}

New users may want to first look through the Siminov Getting Started Guide for basic information as well as tutorials. Even seasoned veterans may want to considering perusing the sections pertaining to build artifacts for any changes.


